SST_patterns

### 2020-01-19 SST_patterns.Rmd
update

```{r}
load("Data/Combined_frequency.RData")
```

>>>>

```{r}
load("Data/Combined_frequency.RData")

# Does not accurately show the months
# Ned to include distance and product

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals)) +
  geom_line(aes(colour = product)) +
  geom_smooth(aes(colour = product), method = "lm") +
  facet_wrap(~site) +
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals)) +
  geom_point(aes(colour = distance)) +
  geom_smooth(aes(colour = distance), method = "lm") +
  facet_wrap(~site)+
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

####

combined_frequency_split <- Combined_frequency %>% 
  separate(date, into = c("month", "year"))

# ggplot(data = combined_frequency_split, aes(x = year, y = number_of_signals)) +
#   geom_line(aes(colour = month)) +
#   geom_smooth(aes(colour = month), method = "lm") +
#   facet_wrap(~site)
```

#Pairwise correlations
Comparing the relaionship of variables within the same sample

  -Correlate the 1st pixel with the second pixel and the first pixel with the last pixel
  -Correlation of the number of frequencies at different distances at each site

```{r}
cor.test(x = Combined_frequency$distance, Combined_frequency$number_of_signals,
    use = "everything", method = "pearson")

slope_calc <- function(df){
  df %>% 
    mutate(row_num = 1:n()) %>% 
    do(mod1 = lm(number_of_signals ~ row_num, data = .),
       mod2 = lm(distance ~ row_num, data = .),
       mod3 = lm(distance ~ number_of_signals, data = .),
       mod4 = cor(.$distance, .$number_of_signals, method = "pearson", use = "complete.obs")[1]) %>% 
    mutate(distance_slope = summary(mod1)$coeff[2],
           signal_slope = summary(mod2)$coeff[2],
           signal_distance_slope = summary(mod3)$coeff[2],
           signal_distance_r = mod4[1],
           signal_distance_r2 = glance(mod3)$adj.r.squared) %>%
    select(-mod1, -mod2, -mod3, -mod4) %>% 
    mutate_if(is.numeric, round, 2)
}

distance_corr <- Combined_frequency %>% 
  group_by(site) %>% 
  slope_calc()

#

    #Why are there no signals in 2011 in the SACTN data?
    # Why are some signals detected in the SACTN data? Is this because of the intensity of the signals?

# Reasons why upwelling might be detected at 10km rather than 50km
    # Dome in the isotherm blocking upwelling to reach the surface waters but does occur deeper down
